Case for Support

### 2021-11-16 application/detailsOfResource.tex
Improved caption to fig:proposedBonsaiExtensions

\begin{figure}
    \begin{center}
        \includegraphics[width=5in]{figures/proposed_bonsai_extensions_combined.png}
        \caption{Proposed extensions to Bonsai}
        \label{fig:proposedBonsaiExtensions}
    \end{center}
\end{figure}

>>>>

\begin{figure} \begin{center}
    \includegraphics[width=5in]{figures/proposed_bonsai_extensions_combined.png}
    \caption{Extensions to Bonsai. (A) we propose to integrate machine learning
    functionality into the experimental control loop by building software
    infrastructure to allow Bonsai to communicate with existing machine
    learning software written in Python, R and Matlab. (B) flow chart
    representing the BCI application that we propose to implement with the
    machine learning functionality to be added to Bonsai. (C) Bonsai graphic
    program implementing the BCI application in (B).}

        \label{fig:proposedBonsaiExtensions}
    \end{center}
\end{figure}
